DeepSphere: a graph-based spherical CNN

### 2019-11-14 main.tex
fix climate sphere figure
replace \cite by \citet or \citep

\todo{
\begin{itemize}
% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
% 	\item anonymize DeepSphere citation - Not doing that
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item citet for inline, citep for parenthesis
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method. \nati{I would drop this.}
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot \nati{I would drop this}
	\item result tables: only what supports the main message in the text, everything we have in the appendix \nati{I think this is done now}
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness? \nati{I think this is already done.}
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere. \nati{Where do you want to add them?}
	\item figure placements \nati{Good according to me}
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper \nati{I guess we are not doing that.}
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space. \nati{I think this does not apply anymore}
	%\item shall we still site adam and batch norm? no, mainstream enough
	\item check results for ModelNet40 and integrate in text \nati{I would drop this}
	\item Check that HEALPix is introduced in the introduction
	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.  \nati{Bit syre what you mean here...}
% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned) \nati{I guess we are not doing that}
	\item add it with equivariance error of the convolution to \tabref{cosmo}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
\end{itemize}
}

\todo{
rebuttal:
\begin{itemize}
    \item answer reviewers and commenters [mdeff \& nath]
    \item update the proof [nath \& martino]
    \item better link between the proof and equivarian
    \item publish the code and link it here
	\item swap AR and TC on figure 1
	\item add somewhere: exploit symmetries to reduce sample cost
	\item proposition 1 -> corollary 3.1?
\end{itemize}
}

@@

% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{figure_architecture_v3}
% 	\caption{Example architecture from \cite{perraudin2019deepspherecosmo}.
% 		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
% 		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
% 		\todo{Shall we keep this figure? It's very nice, but we could save space. ML people probably have this in mind.}
% 	}
% 	\label{fig:architecture}
% \end{figure}

@@

We require $F_\V$ to be a suitable subspace of $L^2(\S^2)$ such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
The existence of such a subspace depends on the sampling scheme $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
For most sampling schemes, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
A special case is the equiangular sampling scheme where a sampling theorem holds, and thus a closed form of $T_\V^{-1}$ is known. % \cite{driscoll1994Fouriersphere}
For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}=T_\V f$, thus approximating $T_\V^{-1}$.
For all theoretical considerations, we assume that $F_\V$ exists and $f \in F_\V$.

@@

\subsection{Finding the optimal set of weights}  \label{sec:optimal}
% 1) summary the work of Khasanova
Naturally, \cite{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude and latitude axis. 
Working specifically with the equiangular sampling, they consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, South, West, East).
% and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eqn:weights:khasanova}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

% 2) explain our approach
We chose a different approach and take inspiration from \cite{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eqn:weights:belkin}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.

@@

\paragraph{Theoretical convergence.}
We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling scheme. 
Following their setting, we will work with the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^t f(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
This operator extends the graph Laplacian operator previously defined with the weight scheme of \eqref{eqn:weights:belkin} to each point of the manifold, i.e. the sphere. 
As the radius of the kernel $t$ will be adapted to the number of sample, we also rescale the graph Laplacian operator as
    % \begin{equation}
	% \label{eq:rescaled Heat Kernel Graph Laplacian operator}
	 $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$
	% \end{equation}
Hence, we have the following relations $\b{L}_n^t \b{f} = T_\V L_n^t f$. 
% $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$. \nati{why define this, we are not using it}
Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ as the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
\begin{equation}\label{eq:rotation operator}
	\mathcal R_g f(x) := f(g^{-1}(x)).
\end{equation}
\begin{theorem}
	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that 
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
	\begin{equation*}
		\lim_{n\to\infty}\hat{L}_n^{t_n}f(y) = \triangle_{\S^2}f(y).
	\end{equation*} 
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, the discrete counterpart of $ \mathbf{\hat L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \cite{belkin2007convergence}. This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step toward equivariance. We formalize in the following proposition.
%%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{theorem}\label{theo:equivariance}
Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, the rescaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
\begin{equation*}
\forall y\in\mathbb S^2\quad\left| \mathcal R_g \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R_g f(y) \right| \xrightarrow{n\to\infty}0.
\end{equation*}
\end{theorem}
%%%%%%%%%%%%%%%%%%%%%%% end of link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%

@@

% 3.0) explain how we obtained the figures
In \figref{equivariance_error}, we present the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} computed numerically as a function of the frequency (degree) $\ell$, for different parameter sets of DeepSphere as well as for graph construction of \cite{khasanova2017sphericalcnn}.
The error depends of the number of pixels: $12N_{side}^2$ for HEALPix and $4b^2$ for the equiangular sampling. Here $N_{side}$ and $b$ are the sampling parameters determining their precision.
The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the Healpix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}. 
Using these parameters, the error measured is mostly due to imperfections in the empirical approximation of the Laplace-Beltrami operator and not to the sampling.

% 3.1) explain what the figures tell us
For 8 neighbors, selecting the optimal value of $t$ already leads to an improvement compared to \cite{perraudin2019deepspherecosmo}, whose graph also was constructed to have at maximum 8 neighbors. 
With higher the number of neighbors, the equivariance error decreases by more than one order of magnitude. 
Furthermore, increasing the graph resolution ($N_{side}$) leads to an improvement in the high frequencies as well. 
Increasing the graph resolution of the graph of \cite{khasanova2017sphericalcnn} does not seem to improve its equivariance. We note that in our numerical test, this graph was perfectly equivariant to rotations along the horizontal and vertical axis as it should be by design. Nevertheless, it is simply not equivariant along the last rotation. Such equivariance properties might be sufficient for analysing omnidirectional images (that are naturally aligned on the north-south axis).

@@

The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
As in \citet{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
At each pixel, a ray is traced towards the center of the sphere.
The distance from the sphere to the object forms a depth map.
The $\cos$ and $\sin$ of the surface angle forms two normal maps.
The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
The maps are discretized using either an equiangular grid with bandwidth $b = 64$ ($n = 4 b^2 = 16,384$ pixels) or an HEALPix grid with $N_{side} = 32$ ($n = 12 N_{side}^2 = 12,288$ pixels).

@@

\begin{table}
	\centering
	\begin{tabular}{l l l}
	\toprule
	& accuracy & mAP \\
	\midrule
	%\cite{jiang2019sphericalcnn} (paper) & 94.67 & - \\
	\cite{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
	\cite{cohen2019gauge} (S2R) & 97.5 & 68.6 \\
	\cite{cohen2019gauge} (R2R) & 97.7 & 75.9 \\
	DeepSphere (weighted loss) & $97.8\pm 0.3$ & $77.15\pm 1.94$ \\
	DeepSphere (non-weighted loss) & $87.8\pm 0.5$ & $89.16\pm 1.37$ \\
	\bottomrule
	\end{tabular}
	\caption{
		Results on climate event segmentation: mean accuracy (over TC, AR, BG) and mean average precision (over TC and AR).
		DeepSphere achieves state-of-the-art performance. %, suggesting again that anisotropic filters are not necessary.
	}
	\label{tab:climate}
\end{table}

@@

A potential drawback of graph Laplacian-based approaches is the isotropy of graph filters, reducing in principle the expressive power of the NN.
% in principle -> may in fact not
% Our experiments showed that DeepSphere nonetheless achieved state-of-the-art performance, on par with methods featuring anisotropic filters.
% didn't hurt perf in any experiment
% expressive power / generality / powerful / function approximator
%Why anisotropic filters?
Experiments from \citet{cohen2019gauge} and \citet{boscaini2016anisotropicgraphnn} indeed suggest that more general convolutions achieve better performance.
Our experiments on 3D shapes (\secref{exp:shrec}) and climate (\secref{exp:climate}) however show that DeepSphere's isotropic filters do not hinder performance.
% the SHREC'17 experiment too shows that isotropic filters are sufficient
%Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.
Possible explanations for this discrepancy are that NNs somehow compensate for the lack of anisotropic filters, or that some tasks can be solved with isotropic filters.
% why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
The distortions induced by the icosahedral projection in \citet{cohen2019gauge} or the leakage of curvature information in \citet{boscaini2016anisotropicgraphnn} might also alter performance.
%Further research is needed to determine if anisotropic filters are an unnecessary price to pay or if they are needed in some applications.
% As was recently shown for graph NNs used for graph classification, most general might not be the best, when the ultimate goal is generalization [Andreas paper? + previous by xx]

@@

Leveraging these three operators \cite{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$, where the sampling scheme $\V$ is drawn randomly on the manifold. For this reason, their results are all to be interpreted in a probabilistic sense.
Their proofs consist in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges in probability towards \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$. In particular, this second step is given by the following:
\begin{prop}
[\cite{belkin2005towards}, Proposition 4.4]
Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
\begin{equation}
\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).
\end{equation}
\label{prop:3}
\end{prop}

@@

% it is known that  (\cite{belkin2005towards}) to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\S^2}f(x)$
% where $L_n^t$ is defined as follows:

@@

% brief introduction:
% This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}. This equation, as already explained in \cite{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.

@@

The experiment with the model from \cite{jiang2019sphericalcnn} was rerun in order to obtain the AP metrics, but with a batch size of 64 instead of 256 due to GPU memory limit.

>>>>

\todo{
\begin{itemize}
% 	\item shall we really name it? Or simply reference the general idea of a graph-based spherical CNN. [Yes]
% 	\item adjacency matrix: $A$ instead of $W$? nath: I am for W
% 	\item anonymize DeepSphere citation - Not doing that
% 	\item climate spherical figure: inputs with TC and AR labels superimposed [Frédérick]
	\item More details on related work? Not sure we have the space. If yes, detailed comparison with related work after method. \nati{I would drop this.}
	\item PSD of climate data: how does it compare to cosmo and 3D objects?
	\item align the spheres in figure 1
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item check footnotes
	\item climate data on spectrum plot \nati{I would drop this}
	\item result tables: only what supports the main message in the text, everything we have in the appendix \nati{I think this is done now}
	\item Unify vocabulary. Sampling, discretization, or pixelization of the sphere? Signal, maps, functions. Irregular, uneven. Coarsening, down-sampling.
	\item check English vs American English
	\item unify enumerations. I like (i), (ii), etc.
	\item notation: should we use indices from 1 to n instead of 0 to n-1 for compactness? \nati{I think this is already done.}
	\item add \citet{bruna2013gnn} in equivariance? They were the first to do a spherical CNN with graphs. Graph is built from a uniform random sampling of the sphere. \nati{Where do you want to add them?}
	\item figure placements \nati{Good according to me}
	\item do the experiments on the icosahedral grid with the pooling as defined in the paper \nati{I guess we are not doing that.}
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item check that NN architectures and hyper-params are correctly reported
	\item keep NN architecture and hyper-params in the main text? Move the paragraph to appendix if not enough space. \nati{I think this does not apply anymore}
	%\item shall we still site adam and batch norm? no, mainstream enough
	\item check results for ModelNet40 and integrate in text \nati{I would drop this}
	\item Check that HEALPix is introduced in the introduction
	\item heuristic used to set the kernel width in v1. Add values to \figref{kernel_widths} for comparison.  \nati{Bit syre what you mean here...}
% 	\item check experiments section [Frédérick]: all the results numbers and NN + training details
	\item compute the invariance error of the whole NNs (before and after training, invariance can be learned) \nati{I guess we are not doing that}
	\item add it with equivariance error of the convolution to \tabref{cosmo}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
\end{itemize}
}

\todo{
rebuttal:
\begin{itemize}
    \item answer reviewers and commenters [mdeff \& nath]
    \item update the proof [nath \& martino]
    \item better link between the proof and equivarian
    \item publish the code and link it here
	\item add somewhere: exploit symmetries to reduce sample cost
	\item proposition 1 -> corollary 3.1?
	\item \citet{Mudigonda} used Integrated Water Vapor (IWV) only. That most probably is the same as our TMQ, which is most probably the most informative feature. TODO: run ours with TMQ alone.
\end{itemize}
}

@@

% \begin{figure}
% 	\centering
% 	\includegraphics[width=\linewidth]{figure_architecture_v3}
% 	\caption{Example architecture from \citet{perraudin2019deepspherecosmo}.
% 		Global tasks need a spatial summarization: the FCN variant is rotation invariant (and accepts inputs of varying sizes), while the CNN variant is not.
% 		Dense tasks (when the output lives on the sphere, like segmentation) are rotation equivariant.
% 		\todo{Shall we keep this figure? It's very nice, but we could save space. ML people probably have this in mind.}
% 	}
% 	\label{fig:architecture}
% \end{figure}

@@

We require $F_\V$ to be a suitable subspace of $L^2(\S^2)$ such that $T_\V$ is invertible, i.e., the function $f \in F_\V$ can be unambiguously reconstructed from its sampled values $\b{f}$.
The existence of such a subspace depends on the sampling scheme $\V$, and its characterization is a common problem in signal processing \citep{driscoll1994Fouriersphere}.
For most sampling schemes, it is not known if $F_\V$ exists and hence if $T_\V$ is invertible.
A special case is the equiangular sampling scheme where a sampling theorem holds, and thus a closed form of $T_\V^{-1}$ is known. % \citep{driscoll1994Fouriersphere}
For sampling schemes where no such sampling formula is available, we leverage the discrete SHT to reconstruct $f$ from $\b{f}=T_\V f$, thus approximating $T_\V^{-1}$.
For all theoretical considerations, we assume that $F_\V$ exists and $f \in F_\V$.

@@

\subsection{Finding the optimal set of weights}  \label{sec:optimal}
% 1) summary the work of Khasanova
Naturally, \citet{khasanova2017sphericalcnn} designed a Laplacian $\b{L}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude and latitude axis. 
Working specifically with the equiangular sampling, they consider the set $\mathcal{G}$ of all the possible graphs where each node is connected only to four of its nearest neighbours (North, South, West, East).
% and propose a weighting scheme $w_{ij}$ that minimizes \eqref{eq:equivariance error} for specific rotations on the longitude latitude axis.
Their approach leads to weights $w_{ij}$ inversely proportional to the Euclidean distance between vertices:
\begin{equation} \label{eqn:weights:khasanova}
	w_{ij} = \frac{1}{\norm{x_i-x_j}}
\end{equation}

% 2) explain our approach
We chose a different approach and take inspiration from \citet{belkin2005towards}, which proves that for a random \emph{uniform sampling} scheme the graph Laplacian converges toward the Laplace-Beltrami operator $\Delta_{\mathbb{S}^2}$ as the number of sampling points goes to infinity.
This convergence result is important as a) $\Delta_{\mathbb{S}^2}$ commutes with rotation ($\Delta_{\mathbb{S}^2}R(g) = R(g)\Delta_{\mathbb{S}^2}$) and b) is diagonalized by the spherical harmonics.
In this case the weighting scheme is full (every node is connected to every node) and is based on the exponential kernel:
\begin{equation} \label{eqn:weights:belkin}
w_{ij} = e^{-\frac{1}{4t} \norm{x_i-x_j}^2}
\end{equation}
In practice, because of the exponential, most of the weights are very close to $0$. Hence, to optimize for computational efficiency, we limit ourselves to only the $k$ nearest neighbors.
Given $k$, the optimal $t$ is found by searching for the minimizer of \eqref{eq:mean equivariance error}.
\Figref{kernel_widths} shows the optimal kernel widths found for various resolutions of the HEALPix grid.

@@

\paragraph{Theoretical convergence.}
We extend the work of \citep{belkin2005towards} to a sufficiently regular, deterministic sampling scheme. 
Following their setting, we will work with the extended graph Laplacian operator as the linear operator $L_n^t: L^{2}(\mathcal{M}) \rightarrow L^{2}(\mathcal{M})$ such that
	\begin{equation}
	\label{eq:Heat Kernel Graph Laplacian operator}
	 L_n^t f(y) := \frac{1}{n}\sum_{i=0}^{n-1} e^{ -\frac{\|x_i-y\|^2}{4t}} \left(f(y)-f(x_i)\right).
	\end{equation}
This operator extends the graph Laplacian operator previously defined with the weight scheme of \eqref{eqn:weights:belkin} to each point of the manifold, i.e. the sphere. 
As the radius of the kernel $t$ will be adapted to the number of sample, we also rescale the graph Laplacian operator as
    % \begin{equation}
	% \label{eq:rescaled Heat Kernel Graph Laplacian operator}
	 $\hat{L}_n^t := \frac{|\mathbb S^2|}{4\pi t^2}L_n^t$
	% \end{equation}
Hence, we have the following relations $\b{L}_n^t \b{f} = T_\V L_n^t f$. 
% $\b{\hat L} = \frac{|\mathbb S^2|}{4\pi t^2}\b L_n^t$. \nati{why define this, we are not using it}
Given a sampling scheme $\V = \{x_0, \dots, x_{n-1}\}$, we define $\sigma_i$ to be the patch of the surface of the sphere corresponding to $x_i$, $A_i$ its corresponding area, and $d_i$ as the largest distance between the center $x_i$ and any point on the surface $\sigma_i$.
 Define $d^{(n)} := \max_{i=0, \dots, n}d_i$ and $A^{(n)}=\max_{i=0, \dots, n}A_i$.
Given any rotation $g\in SO(3)$, we define the corresponding rotation operator $\mathcal R_g$ such that for any function $f$ on the sphere
\begin{equation}\label{eq:rotation operator}
	\mathcal R_g f(x) := f(g^{-1}(x)).
\end{equation}
\begin{theorem}
	For a sampling $\V = \{x_i\in\S^2\}_{i=0}^{n-1}$ of the sphere that is equi-area and such that $d^{(n)} \leq \frac{C}{n^\alpha}, \ \alpha\in (0,\linefrac{1}{2}]$, for all $f: \S^2 \rightarrow \R$ Lipschitz with respect to the Euclidean distance in $\R^3$, for all $y\in\S^2$, there exists a sequence $t_n = n^\beta$, $\beta\in\mathbb R$ such that 
% 	the rescaled Heat Kernel Graph Laplacian $\frac{|\S^2|}{4\pi t_n^2}\b {L}^t_n$ converges pointwise to the Laplace Beltrami operator on the sphere $\Delta{\S^2}$  
	\begin{equation*}
		\lim_{n\to\infty}\hat{L}_n^{t_n}f(y) = \triangle_{\S^2}f(y).
	\end{equation*} 
	\label{theo:pointwise convergence for a regular sampling}
\end{theorem}
As a direct implication of this theorem, the discrete counterpart of $ \mathbf{\hat L}$ converges pointwise towards the Laplace-Beltrami operator ($\Delta_{\S^2}$) in the sense explained in \citep{belkin2007convergence}. This operator commutes with rotation and hence Theorem \ref{theo:pointwise convergence for a regular sampling} is a strong step toward equivariance. We formalize in the following proposition.
%%%%%%%%%%%%%%%%%%%%%%%  link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%
\begin{theorem}\label{theo:equivariance}
Under the hypothesis of theorem \ref{theo:pointwise convergence for a regular sampling}, the rescaled graph Laplacian commutes with any rotation, in the limit of infinite sampling, i.e.,
\begin{equation*}
\forall y\in\mathbb S^2\quad\left| \mathcal R_g \hat L_n^{t_n} f (y) - \hat L_n^{t_n} \mathcal R_g f(y) \right| \xrightarrow{n\to\infty}0.
\end{equation*}
\end{theorem}
%%%%%%%%%%%%%%%%%%%%%%% end of link between consistency and equivariance %%%%%%%%%%%%%%%%%%%%%%%%%

@@

% 3.0) explain how we obtained the figures
In \figref{equivariance_error}, we present the equivariance error $\bar{E}_{\b L,C(\ell)}$ \eqref{eq:mean equivariance error} computed numerically as a function of the frequency (degree) $\ell$, for different parameter sets of DeepSphere as well as for graph construction of \citet{khasanova2017sphericalcnn}.
The error depends of the number of pixels: $12N_{side}^2$ for HEALPix and $4b^2$ for the equiangular sampling. Here $N_{side}$ and $b$ are the sampling parameters determining their precision.
The frequencies $\ell$ of the monochromatic signals were chosen in the range $(0,\  3N_{side}-1)$ for the Healpix sampling, and in the range $(0, b)$ for the equiangular sampling, to allow for an almost perfect implementation (up to numerical errors) of the operator $\b{R}_\V$ in equation \eqref{eq:mean equivariance error} \citep{gorski1999healpixprimer}. 
Using these parameters, the error measured is mostly due to imperfections in the empirical approximation of the Laplace-Beltrami operator and not to the sampling.

% 3.1) explain what the figures tell us
For 8 neighbors, selecting the optimal value of $t$ already leads to an improvement compared to \citet{perraudin2019deepspherecosmo}, whose graph also was constructed to have at maximum 8 neighbors. 
With higher the number of neighbors, the equivariance error decreases by more than one order of magnitude. 
Furthermore, increasing the graph resolution ($N_{side}$) leads to an improvement in the high frequencies as well. 
Increasing the graph resolution of the graph of \citet{khasanova2017sphericalcnn} does not seem to improve its equivariance. We note that in our numerical test, this graph was perfectly equivariant to rotations along the horizontal and vertical axis as it should be by design. Nevertheless, it is simply not equivariant along the last rotation. Such equivariance properties might be sufficient for analysing omnidirectional images (that are naturally aligned on the north-south axis).

@@

The SHREC'17 shape retrieval contest \citep{shrec17} contains 51,300 randomly oriented 3D models from ShapeNet \citep{shapenet}, to be classified in 55 categories (tables, lamps, airplanes, etc.).
As in \citep{cohen2018sphericalcnn}, objects are represented by 6 spherical maps.
At each pixel, a ray is traced towards the center of the sphere.
The distance from the sphere to the object forms a depth map.
The $\cos$ and $\sin$ of the surface angle forms two normal maps.
The same is done for the object's convex hull.\footnote{Albeit we didn't observe much improvement by using the convex hull.}
The maps are discretized using either an equiangular grid with bandwidth $b = 64$ ($n = 4 b^2 = 16,384$ pixels) or an HEALPix grid with $N_{side} = 32$ ($n = 12 N_{side}^2 = 12,288$ pixels).

@@

\begin{table}
	\centering
	\begin{tabular}{l l l}
	\toprule
	& accuracy & mAP \\
	\midrule
	%\citet{jiang2019sphericalcnn} (paper) & 94.67 & - \\
	\citet{jiang2019sphericalcnn} (rerun) & 94.95 & 38.41 \\
	\citet{cohen2019gauge} (S2R) & 97.5 & 68.6 \\
	\citet{cohen2019gauge} (R2R) & 97.7 & 75.9 \\
	DeepSphere (weighted loss) & $97.8\pm 0.3$ & $77.15\pm 1.94$ \\
	DeepSphere (non-weighted loss) & $87.8\pm 0.5$ & $89.16\pm 1.37$ \\
	\bottomrule
	\end{tabular}
	\caption{
		Results on climate event segmentation: mean accuracy (over TC, AR, BG) and mean average precision (over TC and AR).
		DeepSphere achieves state-of-the-art performance. %, suggesting again that anisotropic filters are not necessary.
	}
	\label{tab:climate}
\end{table}

@@

A potential drawback of graph Laplacian-based approaches is the isotropy of graph filters, reducing in principle the expressive power of the NN.
% in principle -> may in fact not
% Our experiments showed that DeepSphere nonetheless achieved state-of-the-art performance, on par with methods featuring anisotropic filters.
% didn't hurt perf in any experiment
% expressive power / generality / powerful / function approximator
%Why anisotropic filters?
Experiments from \citet{cohen2019gauge} and \citet{boscaini2016anisotropicgraphnn} indeed suggest that more general convolutions achieve better performance.
Our experiments on 3D shapes (\secref{exp:shrec}) and climate (\secref{exp:climate}) however show that DeepSphere's isotropic filters do not hinder performance.
% the SHREC'17 experiment too shows that isotropic filters are sufficient
%Works on shape alignment indicates that anisotropic filters achieve better performance \todo{[Bronstein]}.
Possible explanations for this discrepancy are that NNs somehow compensate for the lack of anisotropic filters, or that some tasks can be solved with isotropic filters.
% why: icosahedron, can do anisotropy with isotropy + non-linearity + pooling
The distortions induced by the icosahedral projection in \citep{cohen2019gauge} or the leakage of curvature information in \citep{boscaini2016anisotropicgraphnn} might also alter performance.
%Further research is needed to determine if anisotropic filters are an unnecessary price to pay or if they are needed in some applications.
% As was recently shown for graph NNs used for graph classification, most general might not be the best, when the ultimate goal is generalization [Andreas paper? + previous by xx]

@@

Leveraging these three operators, \citet{belkin2005towards, belkin2007convergence} have build proofs of both pointwise and spectral convergence of the extended graph Laplacian towards the Laplace-Beltrami operator in the general setting of any compact, closed and infinitely differentiable maniform $\mathcal M$, where the sampling scheme $\V$ is drawn randomly on the manifold. For this reason, their results are all to be interpreted in a probabilistic sense.
Their proofs consist in establishing that \eqref{eq:Heat Kernel Graph Laplacian operator} converges in probability towards \eqref{eq:Functional approximation to the Laplace-Beltrami operator} as $n\rightarrow \infty$ and \eqref{eq:Functional approximation to the Laplace-Beltrami operator} converges toward \eqref{eq:laplace-beltrami} as $t\rightarrow 0$. In particular, this second step is given by the following:
\begin{prop}
[\citet{belkin2005towards}, Proposition 4.4]
Let $\mathcal{M}$ be a $k$-dimensional compact smooth manifold embedded in some Euclidean space $\mathbb{R}^N$, and fix $y\in\mathcal{M}$. Let $f\in\mathcal{C}_\infty(\mathcal{M)}$. Then
\begin{equation}
\frac{1}{t}\frac{1}{(4\pi t)^{k/2}} L^tf(y) \xrightarrow{t\to 0 } \frac{1}{\text{vol}(\mathcal M)}\Delta_{\mathcal M}f(y).
\end{equation}
\label{prop:3}
\end{prop}

@@

% it is known that \citep{belkin2005towards} to prove the convergence of $(\b {L}_n^t \b f) _i$ to $\Delta_{\S^2}f(x_i)$ it is sufficient to prove the convergence of its continuous counterpart $L_n^tf(x)$ to $\Delta_{\S^2}f(x)$
% where $L_n^t$ is defined as follows:

@@

% brief introduction:
% This proof consists in two steps: first, we prove that $L_n^t \rightarrow L^t$, and second, we use proposition \ref{prop:3} to prove \eqref{eq:continuous convergence}. This equation, as already explained in \citep{belkin2007convergence}, directly implies theorem \ref{theo:pointwise convergence for a regular sampling}.

@@

The experiment with the model from \citet{jiang2019sphericalcnn} was rerun in order to obtain the AP metrics, but with a batch size of 64 instead of 256 due to GPU memory limit.
